---
title: "CellChat_Analysis"
author: "Sida Chen"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(spacexr)
library(Seurat)
library(ggplot2) #for saving result plots
library(CellChat)
library(patchwork)
library(SeuratData)
library(dplyr)
library(purrr)
library(hdf5r)
library(glmGamPoi)
options(stringsAsFactors = FALSE)
ptm = Sys.time()
```

# AK1
## Part I: Data input & processing and initialization of CellChat object
### Load single cell data from Cell Ranger output directory
```{r}
ak1<- Load10X_Spatial(data_dir <- './data/ak1', 
                         filename = "filtered_feature_bc_matrix.h5")


plot1 <- VlnPlot(ak1, features = "nCount_Spatial", pt.size = 0.1) + NoLegend()
plot2 <- SpatialFeaturePlot(ak1, features = "nCount_Spatial") + theme(legend.position = "right")
plot2
```

### Data preprocessing: normalization
```{r}
ak1 = ak1[,unname(which(colSums(GetAssayData(ak1))!=0))]

ak1 <- SCTransform(ak1, assay = "Spatial", verbose = FALSE)
```

### Dimensionality reduction, clustering, and visualization
```{r}
ak1 <- RunPCA(ak1, assay = "SCT", verbose = FALSE)
ak1 <- FindNeighbors(ak1, reduction = "pca", dims = 1:30)
ak1 <- FindClusters(ak1, verbose = FALSE)
ak1 <- RunUMAP(ak1, reduction = "pca", dims = 1:30)

color.use <- scPalette(nlevels(ak1)); names(color.use) <- levels(ak1)
Idents(ak1) <- factor(Idents(ak1), levels = levels(Idents(ak1)), labels = c("1", "2", "3", "4", "5", "6", "7"))
Seurat::SpatialDimPlot(ak1, label = T, label.size = 3, cols = color.use, pt.size.factor = 3)
```

### Prepare input data for CelChat analysis
```{r}
data.input1 = Seurat::GetAssayData(ak1, slot = "data", assay = "SCT")
```

### define the meta data
```{r}
meta1 = data.frame(labels = Seurat::Idents(ak1), slices = "slice1", row.names = names(Seurat::Idents(ak1))) # manually create a dataframe consisting of the cell labels
meta1$slices <- factor(meta1$slices)
unique(meta1$labels) # check the cell labels
unique(meta1$slices)
```

### load spatial transcriptomics information
```{r}
spatial.locs1 = Seurat::GetTissueCoordinates(ak1, scale = NULL, cols = c("imagerow", "imagecol")) 
spatial.locs1 <- spatial.locs1[, !colnames(spatial.locs1) %in% "cell"]
```

### Scale factors of spatial coordinates
```{r}
scalefactors1 = jsonlite::fromJSON('{"regist_target_img_scalef": 1.0, "tissue_hires_scalef": 0.6666667, "tissue_lowres_scalef": 0.2, "fiducial_diameter_fullres": 22.741010123623237, "spot_diameter_fullres": 15.160673415748823}')
spot.size = 65 # the theoretical spot size (um) in 10X Visium
conversion.factor1 = spot.size/scalefactors1$spot_diameter_fullres
spatial.factors1 = data.frame(ratio = conversion.factor1, tol = spot.size/2)
```

### Create a CellChat object
```{r}
cellchat1 <- createCellChat(object = data.input1, meta = meta1, group.by = "labels",
                           datatype = "spatial", coordinates = spatial.locs1, spatial.factors = spatial.factors1)

```

### Set the ligand-receptor interaction database
```{r}
CellChatDB <- CellChatDB.human
showDatabaseCategory(CellChatDB)
cellchat1@DB <- CellChatDB
```

### Preprocessing the expression data for cell-cell communication analysis
```{r}
cellchat1 <- subsetData(cellchat1)
future::plan("multisession", workers = 4) 
cellchat1 <- identifyOverExpressedGenes(cellchat1)
cellchat1 <- identifyOverExpressedInteractions(cellchat1)
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))
```

## Part II: Inference of cell-cell communication network
```{r}
ptm = Sys.time()

cellchat1 <- computeCommunProb(cellchat1, type = "truncatedMean", trim = 0.1, 
                              distance.use = TRUE, interaction.range = 250, scale.distance = 0.01,
                              contact.dependent = TRUE, contact.range = 100)
```

### Filter out the cell-cell communication if there are only few number of cells in certain cell groups
```{r}
cellchat1 <- filterCommunication(cellchat1, min.cells = 10)
```

### Extract the inferred cellular communication network as a data frame
```{r}
df.net1 <- subsetCommunication(cellchat1)
```

### Infer the cell-cell communication at a signaling pathway level
```{r}
cellchat1 <- computeCommunProbPathway(cellchat1)
```

### Calculate the aggregated cell-cell communication network 
```{r}
cellchat1 <- aggregateNet(cellchat1)

execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))

ptm = Sys.time()

groupSize <- as.numeric(table(cellchat1@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat1@net$count, vertex.weight = rowSums(cellchat1@net$count), weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat1@net$weight, vertex.weight = rowSums(cellchat1@net$weight), weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

netVisual_heatmap(cellchat1, measure = "count", color.heatmap = "Blues")
netVisual_heatmap(cellchat1, measure = "weight", color.heatmap = "Blues")

# sub-dataset
df.net_c12 <- subsetCommunication(cellchat1, sources.use = "2", targets.use = "1") ##gives the inferred cell-cell communications sending from cell groups 2 (dermis) to cell groups 1 (dysplastic).
df.net_c21 <- subsetCommunication(cellchat1, sources.use = "1", targets.use = "2") ##gives the inferred cell-cell communications sending from cell groups 1 (dysplastic) to cell groups 2 (dermis).
```

## Visualize cell-cell communication mediated by multiple ligand-receptors or signaling pathways
### Bubble plot
(1) show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
```{r}
par(mfrow=c(1,1))
netVisual_bubble(cellchat1, sources.use = "2", targets.use = c("1":"6"), remove.isolate = FALSE, dot.size.min = 5, dot.size.max = 10, font.size = 17, grid.on = TRUE, color.grid = "black")
netVisual_bubble(cellchat1, sources.use = "1", targets.use = c("1":"6"), remove.isolate = FALSE, dot.size.min = 5, dot.size.max = 10, font.size = 17, grid.on = TRUE, color.grid = "black")
```


# AK2
## Part I: Data input & processing and initialization of CellChat object
### Load single cell data from Cell Ranger output directory
```{r}
ak2<- Load10X_Spatial(data_dir <- './data/ak2', 
                         filename = "filtered_feature_bc_matrix.h5")


plot3 <- VlnPlot(ak2, features = "nCount_Spatial", pt.size = 0.1) + NoLegend()
plot4 <- SpatialFeaturePlot(ak2, features = "nCount_Spatial") + theme(legend.position = "right")
plot4
```

### Data preprocessing: normalization
```{r}
options(future.globals.maxSize = 4 * 1024 * 1024 * 1024) # Set to 4 GiB


ak2 = ak2[,unname(which(colSums(GetAssayData(ak2))!=0))]

ak2 <- SCTransform(ak2, assay = "Spatial", verbose = FALSE)
```

### Dimensionality reduction, clustering, and visualization
```{r}
ak2 <- RunPCA(ak2, assay = "SCT", verbose = FALSE)
ak2 <- FindNeighbors(ak2, reduction = "pca", dims = 1:30)
ak2 <- FindClusters(ak2, verbose = FALSE)
ak2 <- RunUMAP(ak2, reduction = "pca", dims = 1:30)

color.use <- scPalette(nlevels(ak2)); names(color.use) <- levels(ak2)
Idents(ak2) <- factor(Idents(ak2), levels = levels(Idents(ak2)), labels = c("1", "2", "3", "4", "5", "6", "7", "8"))
Seurat::SpatialDimPlot(ak2, label = T, label.size = 3, cols = color.use, pt.size.factor = 3)
```

### Prepare input data for CelChat analysis
```{r}
data.input2 = Seurat::GetAssayData(ak2, slot = "data", assay = "SCT")
```

### define the meta data
```{r}
meta2 = data.frame(labels = Seurat::Idents(ak2), slices = "slice1", row.names = names(Seurat::Idents(ak2))) # manually create a dataframe consisting of the cell labels
meta2$slices <- factor(meta2$slices)
unique(meta2$labels) # check the cell labels
unique(meta2$slices)
```

### load spatial transcriptomics information
```{r}
spatial.locs2 = Seurat::GetTissueCoordinates(ak2, scale = NULL, cols = c("imagerow", "imagecol")) 
spatial.locs2 <- spatial.locs2[, !colnames(spatial.locs2) %in% "cell"]
```

### Scale factors of spatial coordinates
```{r}
scalefactors2 = jsonlite::fromJSON('{"regist_target_img_scalef": 1.0, "tissue_hires_scalef": 0.6666667, "tissue_lowres_scalef": 0.2, "fiducial_diameter_fullres": 22.741010123623237, "spot_diameter_fullres": 15.160673415748823}')
spot.size = 65 # the theoretical spot size (um) in 10X Visium
conversion.factor2 = spot.size/scalefactors2$spot_diameter_fullres
spatial.factors2 = data.frame(ratio = conversion.factor2, tol = spot.size/2)
```

### Create a CellChat object
```{r}
cellchat2 <- createCellChat(object = data.input2, meta = meta2, group.by = "labels",
                           datatype = "spatial", coordinates = spatial.locs2, spatial.factors = spatial.factors2)

```

### Set the ligand-receptor interaction database
```{r}
CellChatDB <- CellChatDB.human
showDatabaseCategory(CellChatDB)
cellchat2@DB <- CellChatDB
```

### Preprocessing the expression data for cell-cell communication analysis
```{r}
cellchat2 <- subsetData(cellchat2)
future::plan("multisession", workers = 4) 
cellchat2 <- identifyOverExpressedGenes(cellchat2)
cellchat2 <- identifyOverExpressedInteractions(cellchat2)
execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))
```

## Part II: Inference of cell-cell communication network
```{r}
ptm = Sys.time()

cellchat2 <- computeCommunProb(cellchat2, type = "truncatedMean", trim = 0.1, 
                              distance.use = TRUE, interaction.range = 250, scale.distance = 0.01,
                              contact.dependent = TRUE, contact.range = 100)
```

### Filter out the cell-cell communication if there are only few number of cells in certain cell groups
```{r}
cellchat2 <- filterCommunication(cellchat2, min.cells = 10)
```

### Extract the inferred cellular communication network as a data frame
```{r}
df.net2 <- subsetCommunication(cellchat2)
```

### Infer the cell-cell communication at a signaling pathway level
```{r}
cellchat2 <- computeCommunProbPathway(cellchat2)
```

### Calculate the aggregated cell-cell communication network 
```{r}
cellchat2 <- aggregateNet(cellchat2)

execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))

ptm = Sys.time()

groupSize <- as.numeric(table(cellchat2@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat2@net$count, vertex.weight = rowSums(cellchat2@net$count), weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat2@net$weight, vertex.weight = rowSums(cellchat2@net$weight), weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

netVisual_heatmap(cellchat2, measure = "count", color.heatmap = "Blues")
netVisual_heatmap(cellchat2, measure = "weight", color.heatmap = "Blues")

# sub-dataset
df.net_c51 <- subsetCommunication(cellchat2, sources.use = "5", targets.use = "1") ##gives the inferred cell-cell communications sending from cell groups 5 (dermis) to cell groups 1 (dysplastic).
df.net_c15 <- subsetCommunication(cellchat2, sources.use = "1", targets.use = "5") ##gives the inferred cell-cell communications sending from cell groups 1 (dysplastic) to cell groups 5 (dermis).
```

## Visualize cell-cell communication mediated by multiple ligand-receptors or signaling pathways
### Bubble plot
(1) show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
```{r}
par(mfrow=c(1,1))
netVisual_bubble(cellchat2, sources.use = "5", targets.use = c("1":"8"), remove.isolate = FALSE, dot.size.min = 5, dot.size.max = 10, font.size = 17, grid.on = TRUE, color.grid = "black")
netVisual_bubble(cellchat2, sources.use = "1", targets.use = c("1":"8"), remove.isolate = FALSE, dot.size.min = 5, dot.size.max = 10, font.size = 17, grid.on = TRUE, color.grid = "black")
```


# AK4 lower part
## Part I: Data input & processing and initialization of CellChat object
### Load single cell data from Cell Ranger output directory
```{r}
ak4_d<- Load10X_Spatial(data_dir <- './data/ak4', 
                         filename = "filtered_feature_bc_matrix.h5",
  assay = "Spatial")

plot5 <- VlnPlot(ak4_d, features = "nCount_Spatial", pt.size = 0.1) + NoLegend()
plot6 <- SpatialFeaturePlot(ak4_d, features = "nCount_Spatial") + theme(legend.position = "right")
plot6
```

### Data preprocessing: normalization
```{r}
ak4_d = ak4_d[,unname(which(colSums(GetAssayData(ak4_d))!=0))]

ak4_d <- SCTransform(ak4_d, assay = "Spatial", verbose = FALSE)
```

### Dimensionality reduction, clustering, and visualization
```{r}
ak4_d <- RunPCA(ak4_d, assay = "SCT", verbose = FALSE)
ak4_d <- FindNeighbors(ak4_d, reduction = "pca", dims = 1:30)
ak4_d <- FindClusters(ak4_d, verbose = FALSE)
ak4_d <- RunUMAP(ak4_d, reduction = "pca", dims = 1:30)

custom_colors <- c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#FF7F00", "#BC9DCC", "#A65628", "#66C2A5", "#999999"); names(custom_colors) <- levels(ak4_d)

Seurat::SpatialDimPlot(ak4_d, pt.size.factor = 4, label = T, label.size = 3, cols = custom_colors)
```

### Prepare input data for CelChat analysis
```{r}
data.input4d = Seurat::GetAssayData(ak4_d, slot = "data", assay = "SCT")
```

### define the meta data
```{r}
meta4d = data.frame(labels = Seurat::Idents(ak4_d), slices = "slice1", row.names = names(Seurat::Idents(ak4_d))) # manually create a dataframe consisting of the cell labels
meta4d$slices <- factor(meta4d$slices)
unique(meta4d$labels) # check the cell labels
unique(meta4d$slices)
```

### load spatial transcriptomics information
```{r}
spatial.locs4d = Seurat::GetTissueCoordinates(ak4_d, scale = NULL, cols = c("imagerow", "imagecol")) 
spatial.locs4d <- spatial.locs4d[, !colnames(spatial.locs4d) %in% "cell"]
```

### Scale factors of spatial coordinates
```{r}
scalefactors4d = jsonlite::fromJSON('{"regist_target_img_scalef": 1.0, "tissue_hires_scalef": 0.6666667, "tissue_lowres_scalef": 0.2, "fiducial_diameter_fullres": 22.766434, "spot_diameter_fullres": 15.177623}')
spot.size = 65 # the theoretical spot size (um) in 10X Visium
conversion.factor4d = spot.size/scalefactors4d$spot_diameter_fullres
spatial.factors4d = data.frame(ratio = conversion.factor4d, tol = spot.size/2)

d.spatial <- computeCellDistance(coordinates = spatial.locs4d, ratio = spatial.factors4d$ratio, tol = spatial.factors4d$tol)
min(d.spatial[d.spatial!=0])
```

### Create a CellChat object
```{r}
levels(meta4d$labels)[levels(meta4d$labels)=='0'] <- "9"
cellchat4d <- createCellChat(object = data.input4d, meta = meta4d, group.by = "labels",
                           datatype = "spatial", coordinates = spatial.locs4d, spatial.factors = spatial.factors4d)
```

### Set the ligand-receptor interaction database
```{r}
CellChatDB <- CellChatDB.human
showDatabaseCategory(CellChatDB)
cellchat4d@DB <- CellChatDB
```

### Preprocessing the expression data for cell-cell communication analysis
```{r}
cellchat4d <- subsetData(cellchat4d)
future::plan("multisession", workers = 4) 
cellchat4d <- identifyOverExpressedGenes(cellchat4d)
cellchat4d <- identifyOverExpressedInteractions(cellchat4d)

execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))
```


## Part II: Inference of cell-cell communication network
```{r}
ptm = Sys.time()

cellchat4d <- computeCommunProb(cellchat4d, type = "truncatedMean", trim = 0.1, 
                              distance.use = TRUE, interaction.range = 250, scale.distance = 0.01,
                              contact.dependent = TRUE, contact.range = 100)
```
### Filter out the cell-cell communication if there are only few number of cells in certain cell groups
```{r}
cellchat4d <- filterCommunication(cellchat4d, min.cells = 10)
```

### Extract the inferred cellular communication network as a data frame
```{r}
df.net4d <- subsetCommunication(cellchat4d)
```

### Infer the cell-cell communication at a signaling pathway level
```{r}
cellchat4d <- computeCommunProbPathway(cellchat4d)
```

### Calculate the aggregated cell-cell communication network 
```{r}
cellchat4d <- aggregateNet(cellchat4d)

execution.time = Sys.time() - ptm
print(as.numeric(execution.time, units = "secs"))

ptm = Sys.time()

groupSize4d <- as.numeric(table(cellchat4d@idents))
par(mfrow = c(1,2), xpd=TRUE)
netVisual_circle(cellchat4d@net$count, vertex.weight = rowSums(cellchat4d@net$count), weight.scale = T, label.edge= F, title.name = "Number of interactions")
netVisual_circle(cellchat4d@net$weight, vertex.weight = rowSums(cellchat4d@net$weight), weight.scale = T, label.edge= F, title.name = "Interaction weights/strength")

netVisual_heatmap(cellchat4d, measure = "count", color.heatmap = "Blues")
netVisual_heatmap(cellchat4d, measure = "weight", color.heatmap = "Blues")

# sub-dataset
df.net4d_35 <- subsetCommunication(cellchat4d, sources.use = "3", targets.use = "5") ##gives the inferred cell-cell communications sending from cell groups 3 (upper dermis) to cell groups 5 (dysplastic epidermis).
df.net4d_53 <- subsetCommunication(cellchat4d, sources.use = "5", targets.use = "3") ##gives the inferred cell-cell communications sending from cell groups 5 to cell groups 3.
```

## Visualize cell-cell communication mediated by multiple ligand-receptors or signaling pathways
### Bubble plot
(1) show all the significant interactions (L-R pairs) from some cell groups (defined by 'sources.use') to other cell groups (defined by 'targets.use')
```{r}
par(mfrow=c(1,1))
netVisual_bubble(cellchat4d, sources.use = "3", targets.use = c("1":"9"), remove.isolate = FALSE)
netVisual_bubble(cellchat4d, sources.use = "5", targets.use = c("1":"9"), remove.isolate = FALSE)
```

